Stepwise Multiple Regressions

### 2021-02-10 Stepwise Multiple Regressions.Rmd
minor change to make sure plots match

@@

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```
```{r}
#alternative method using ggpredict
require(ggeffects)
require(ggdark)
require(ggsci)
ggpredict(m1_crust_model_dose)
df <- ggpredict(m1_crust_model_dose, se = TRUE)
df <- ggpredict(m1_crust_model_dose,terms=c("logdose.mg.L.master", "size.length.um.used.for.conversions"))

>>>>

```{r}
#Plots
ggPredict(m1_crust_model_dose,
          colorn=200,
 #         jitter=TRUE, 
point = FALSE,
          interactive = FALSE, 
show.summary = TRUE,
#digits = 3, 
se = FALSE)
```

```{r}
#particle couunt
#Select the columns that we want to feed into the model for simplicity
m1_crust_part <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.particles.mL.master = log10(dose.particles.mL.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.particles.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_particles <- glm(effect_10 ~ logdose.particles.mL.master * size.length.um.used.for.conversions, data = m1_crust_part, na.action = "na.exclude", family = "binomial")

summary(m1_crust_model_particles)
```
plot
```{r}
ggPredict(m1_crust_model_particles, colorn=1000)
```
### volume
```{r}
#particle couunt
#Select the columns that we want to feed into the model for simplicity
m1_crust_volume <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.um3.mL.master = log10(dose.um3.mL.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.um3.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

#Fit the full model
m1_crust_model_volume <- glm(effect_10 ~ logdose.um3.mL.master * size.length.um.used.for.conversions, data = m1_crust_volume, na.action = "na.exclude", family = "binomial")

summary(m1_crust_model_volume)
```
plot
```{r}
ggPredict(m1_crust_model_volume, colorn=500)
```

```{r}
#alternative method using ggplot

#get probabilities
m1 <- m1_crust %>% 
  mutate(prob = predict(m1_crust_model_dose,
                        type = "response"))

# plot
ggplot(m1, aes(x = logdose.mg.L.master, y = effect_10, color = size.length.um.used.for.conversions))+
  geom_jitter() +
  geom_smooth(method = 'glm',
              aes(x = logdose.mg.L.master, y = prob), #use predicted NOEC probability
              method.args = list(family = binomial(link = 'logit')),
              se = FALSE, color = 'red') #+
  # geom_smooth(method = 'glm',
  #             method.args = list(family = binomial(link = 'probit')),
  #             se = FALSE, color = 'green') +
  # stat_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE)
```

```{r}
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

@@

```{r}
#alternative method using ggpredict
require(ggeffects)
require(ggdark)
require(ggsci)
ggpredict(m1_crust_model_dose)
df <- ggpredict(m1_crust_model_dose, se = TRUE)
df <- ggpredict(m1_crust_model_dose,terms=c("logdose.mg.L.master", "size.length.um.used.for.conversions"))
